\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-02 coq-example.tex
Recheck the number Removing line number from type info.

Our formulation for the base STLC family is around 400+ LOCs; each families implementing a single feature takes around 100~300 LOCs.

@@

Thus, to implement this generic abstract interpreter, we need to postulate the abstract value and their mathematical property. Then we need to prove the abstract interpreter is \textbf{sound and terminating}  with the help of these postulations. Then for concrete analyzer, we only need to instantiate these postulation. The construction and proof of soundness uses "FInduction" and "FRecursion". "analyze_soundness" is saying if 
It takes about 300+ LOCs. 
% This example shows how
% to use family inheritance to extend a concrete interpreter with abstract
% interpreters. 
% This example also shows in this family polymoprhism framework we can reason about "Lang" with computation details being abstracted.

>>>>

Our formulation for the base STLC family is around 400 LOCs; each families implementing a single feature takes 100\~250 LOCs.

@@

Thus, to implement this generic abstract interpreter, we need to postulate the abstract value and their mathematical property. Then we need to prove the abstract interpreter is \textbf{sound and terminating}  with the help of these postulations. In our implementation, this postulation happens in "absStateData" where we indicate the "lift" of concrete interpretation and the mathematical properties these lifted should satisfy. Then for concrete analyzer, we only need to instantiate these postulation. The construction and proof of soundness uses "FInduction" and "FRecursion", mainly on "exp" and "stmt". 
It takes about 300+ LOCs. 
% This example shows how
% to use family inheritance to extend a concrete interpreter with abstract
% interpreters. 
% This example also shows in this family polymoprhism framework we can reason about "Lang" with computation details being abstracted.
